---
title: "HW4_Xu_Peng"
author: "Peng Xu"
date: "2017/9/24"
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(ggExtra)
library(MASS)
library(xlsx)

library(ggplot2)
library(tidyr)

knitr::opts_chunk$set(echo = TRUE)

scatterBarNorm <- function(x, dcol="blue", lhist=20, num.dnorm=5*lhist, ...){
    ## check input
    stopifnot(ncol(x)==2)
    ## set up layout and graphical parameters
    layMat <- matrix(c(2,0,1,3), ncol=2, byrow=TRUE)
    layout(layMat, widths=c(5/7, 2/7), heights=c(2/7, 5/7))
    ospc <- 0.5 # outer space
    pext <- 4 # par extension down and to the left
    bspc <- 1 # space between scatter plot and bar plots
    par. <- par(mar=c(pext, pext, bspc, bspc),
                oma=rep(ospc, 4)) # plot parameters
    ## scatter plot
    plot(x, xlim=range(x[,1]), ylim=range(x[,2]), pch=20, ...)
    ## 3) determine barplot and height parameter
    ## histogram (for barplot-ting the density)
    xhist <- hist(x[,1], plot=FALSE, breaks=seq(from=min(x[,1]),
                to=max(x[,1]),  length.out=lhist))
    yhist <- hist(x[,2], plot=FALSE, breaks=seq(from=min(x[,2]),
                to=max(x[,2]),  length.out=lhist)) # note: this uses probability=TRUE
    ## determine the plot range and all the things needed for the barplots and lines
    xx <- seq(min(x[,1]), max(x[,1]), length.out=num.dnorm) # evaluation points for the overlaid density
    xy <- dnorm(xx, mean=mean(x[,1]), sd=sd(x[,1])) # density points
    yx <- seq(min(x[,2]), max(x[,2]), length.out=num.dnorm)
    yy <- dnorm(yx, mean=mean(x[,2]), sd=sd(x[,2]))
    ## barplot and line for x (top)
    par(mar=c(0, pext, 0, 0))
    barplot(xhist$density, axes=FALSE, ylim=c(0, max(xhist$density, xy)),
            space=0, col = "grey") # barplot
    lines(seq(from=0, to=lhist-1, length.out=num.dnorm), xy, col=dcol) # line
    ## barplot and line for y (right)
    par(mar=c(pext, 0, 0, 0))
    barplot(yhist$density, axes=FALSE, xlim=c(0, max(yhist$density, yy)),
            space=0, horiz=TRUE, col = "orange") # barplot
    lines(yy, seq(from=0, to=lhist-1, length.out=num.dnorm), col=dcol) # line
    ## restore parameters
    par(par.)
}
```

# Question 3
The EDA process provide the "rough cut" for a data analysis. According to Roger Peng, six principles should be summarized as followed.
1) show comparison from different aspects.
2) show causality, mechanism. explanation, and systematic structure. Different factors could be connected to explain one phenomena.
3) show multivariate data. It may uncover unexpected relationships with more features.
4) integrate different evidence to a graphic.
5) describe and document the evidence. A graphic should tell a complete story by itself.
6) present graphics with high-quality content


# Question 4

## Part 1
```{r}
prob4_data1 <- read.xlsx("HW4_data.xlsx", sheetIndex = 1)
prob4_data2 <- read.xlsx("HW4_data.xlsx", sheetIndex = 2)
prob4_RawData <- rbind(prob4_data1,prob4_data2)
summary(prob4_RawData)
```

## Part 2
There are three factors: block, depth, phosphate. The block number seems to be the number of different experiment groups, while depth and phosphate are different measurements of each experiment. 


## Part 3

```{r, fig.align='center', fig.width=6, fig.height=4}
CleanData <- gather(prob4_RawData,type,value = measurement, depth,phosphate)
CleanData_n <- transform(CleanData, block = as.factor(block))
CleanData_n <- transform(CleanData_n, type = as.factor(type))
ggplot(CleanData_n, aes(x=block, y=measurement, fill=type))+geom_boxplot()
```


```{r, fig.align='center', fig.width=6, fig.height=4}
Target <- data.frame(cbind(prob4_RawData$depth ,prob4_RawData$phosphate))
scatterBarNorm(Target, xlab=expression(italic(depth)),
                   ylab=expression(italic(phosphate)))
```

## Part 4

```{r, fig.align='center', fig.width=6, fig.height=4}
pairs(prob4_RawData)
```

## Part 5
From the summary plot, the block seems to be index number of groups, while depth and phosphate are measurement values. The distributions of depth and phosphate are very similar and almost follow the normal distribution. 


