---
title: "HW5_Xu_Peng"
author: "Peng Xu"
date: "2017/10/1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 3
A good figure should demonstrate its contents clearly and neatly. It contains all the required elements, such as legend and caption. It is easy for viewers to obtain the overview. 

It also contains important factors and their relationships. It can recover some important details and helps viewers to consider from different aspects.

It would be excellent if the figure exceeds viewers' expectation. Some valuable and surprising results could be revelt from the elements of the figure. 

# Problem 4

## Part a
```{r}
CountSuccess <- function(vec){
    count <- sum(vec)
    return(count)
}
```

## Part b
```{r}
set.seed(12345)
P4b_data <- matrix(rbinom(10, 1, prob = (30:40)/100), nrow = 10,
ncol = 10)
```


## Part c
```{r}
apply(P4b_data,MARGIN = 1, CountSuccess)

apply(P4b_data,MARGIN = 2, CountSuccess)


```
It is observed that the columns of matrix is simply ten replicates of one experiment set. The list of different probabilities's results are not generated. 

## Part d

```{r}
GenerateRandom <- function(p){
    return(rbinom(10, 1, prob = p))
}

ProbList <- c(30:40)/100
ProbList <- matrix(ProbList, nrow = 1)

ResultMatrix <- apply(ProbList, MARGIN = 2 ,GenerateRandom)
row.names(ResultMatrix)<-c('E1','E2','E3','E4','E5','E6','E7','E8','E9','E10')
ResultMatrix
```

Then the vectors of different probabilites are shown above.

# Problem 5
```{r}
library("plot3D")
URL <- "http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat"
Starch_raw<-read.table(URL, header=T, skip=0, fill=T, stringsAsFactors = F)

#Starch_raw$starch <- as.factor(Starch_raw$starch)

G<-matrix(c('CA',1,'CO',2,'PO',3),ncol=2,byrow=T)
for (i in 1:length(Starch_raw$starch)) {
  if (Starch_raw$starch[i]%in%G[,1]) {
  Starch_raw$starch[i]=G[which(G[,1]==Starch_raw$starch[i]),2]
  }
}

x <- as.numeric(Starch_raw$starch)
y <- Starch_raw$strength
z <- Starch_raw$thickness

par(mfrow=c(1,3))
scatter3D(x, y, z, colvar = x, phi = 10, theta = 60, col = NULL, 
          breaks = c(0,1,2,3), xlab = 'Starch', ylab = 'Strength', zlab = 'Thickness')
scatter3D(x, y, z, colvar = x, phi = 0, theta = 0, col = NULL, 
          breaks = c(0,1,2,3), xlab = 'Starch', ylab = 'Strength', zlab = 'Thickness')
scatter3D(x, y, z, colvar = x, phi = 0, theta = 90, col = NULL, 
          breaks = c(0,1,2,3), xlab = 'Starch', ylab = 'Strength', zlab = 'Thickness')
```

# Problem 6

## Part a
```{r, include=FALSE}
library(downloader)
library(dplyr)
library(data.table)
download("http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip",
         dest = "us_cities_states.zip")
unzip("us_cities_states.zip", exdir = "D:/Git/STAT_5015_homework")
```

```{r}
states <- fread(input = "./us_cities_and_states/states.sql",
                skip = 19, sep = "'", sep2 = ",", header = F, select = c(2,4))
colnames(states) <- c('State','abbr')

cities1 <- fread(input = "./us_cities_and_states/cities.sql",
                skip = 19, sep = "'", sep2 = ",", header = F, select = c(2,4))
cities2 <- fread(input = "./us_cities_and_states/cities_extended.sql",
                skip = 19, sep = "'", sep2 = ",", header = F, select = c(2,4))

cities <- rbind(cities1,cities2)
colnames(cities) <- c('City','State')

CleanCities <- cities %>%
    group_by(City, State) %>%
    filter(row_number() == 1) %>%
    ungroup()
```

## Part b
The number of cities of all states are shown below.
```{r}
CityNum <- table(CleanCities$State)
CityNum <- CityNum[-40]
CityNum <- CityNum[-8]
CityNum
```

## Part c
```{r}
LetterCount <- function(string){
    LetterList <- c('a','b','c','d','e','f','g','h','i','j','k','l','m','n','o','p','q','r','s','t','u','v','w','x','y','z')
    Result <- as.table(rep(0,26))
    row.names(Result) <- LetterList
    
    sp <- strsplit(tolower(as.character(string)), split="")[[1]]
    for(i in 1:26){
        Result[i] <- length(which(sp == LetterList[i]))
    }
    return(Result)
}

#LetterCount('adsfasdfaa')
```

```{r}

Results <- t(apply(as.matrix(states$State),MARGIN = 1,LetterCount))
Results <- Results[-8,]   # remove DC
head(Results)

temp <- apply(Results,MARGIN = 1, max)
ThreeLetterList <- floor(temp/3)
```

## Part d

```{r, include=FALSE}
# https://cran.r-project.org/web/packages/fiftystater/vignettes/fiftystater.html
library(ggplot2)
library(fiftystater)
```

```{r}
data("fifty_states") # this line is optional due to lazy data loading
crimes <- data.frame(state = tolower(rownames(USArrests)),
USArrests)

StateData <- cbind(crimes,CityNum)
StateData <- cbind(StateData,ThreeLetterList)


# map_id creates the aesthetic mapping to the state name
# column in your data
p <- ggplot(StateData, aes(map_id = state)) + # map points to the fifty_states shape data
geom_map(aes(fill = Freq), map = fifty_states) + expand_limits(x = fifty_states$long,
y = fifty_states$lat) + coord_map() + scale_x_continuous(breaks = NULL) +
scale_y_continuous(breaks = NULL) + labs(x = "", y = "") +
theme(legend.position = "bottom", panel.background = element_blank())
p
# ggsave(plot = p, file =
# 'HW5_Problem6_Plot_Settlage.pdf')


```

```{r}
p <- ggplot(StateData, aes(map_id = state)) + # map points to the fifty_states shape data
geom_map(aes(fill = ThreeLetterList), map = fifty_states) + expand_limits(x = fifty_states$long,
y = fifty_states$lat) + coord_map() + scale_x_continuous(breaks = NULL) +
scale_y_continuous(breaks = NULL) + labs(x = "", y = "") +
theme(legend.position = "bottom", panel.background = element_blank())
p
```



