---
title: "HW2_Xu_Peng"
author: "Peng"
date: "2017/9/11"
output:
  pdf_document: default
---

```{r, include=FALSE}

    library(tidyverse)
    library(beeswarm)
    library(stargazer)
    library(data.table)
    library(lubridate)
    library(knitr)
    library(rmarkdown)
    library(dplyr)
    library(tidyr)
    library(beeswarm)
    library(stargazer)
```


# Problem 4
Version control could help me record and modify any temperate ideas inspired from the lectures and materials. If some problem happens, such as the system breakdown, it is easy to recover the data with version control. And with its help, I can also share my files with other people to make cooperation.


# Problem 5

## Part a
```{r, include=FALSE}
    ########################### 
    #Problem5_Sensory_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
    Sensory_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    Sensory_tidy<-Sensory_raw[-1,]
    Sensory_tidy_a<-filter(.data = Sensory_tidy,V1 %in% 1:10) %>%
                    rename(Item=V1,V1=V2,V2=V3,V3=V4,V4=V5,V5=V6)
    Sensory_tidy_b<-filter(.data = Sensory_tidy,!(V1 %in% 1:10)) %>%
                    mutate(Item=rep(as.character(1:10),each=2)) %>%
                    mutate(V1=as.numeric(V1)) %>%
                    select(c(Item,V1:V5))
    Sensory_tidy<-bind_rows(Sensory_tidy_a,Sensory_tidy_b)
    colnames(Sensory_tidy)<-c("Item",paste("Person",1:5,sep="_"))
    Sensory_tidy<-Sensory_tidy %>%  
        gather(Person,value,Person_1:Person_5) %>%  
        mutate(Person = gsub("Person_","",Person)) %>%
        arrange(Item)
    
    ########################### 
```

```{r, echo=FALSE}

    knitr::kable(summary(Sensory_tidy), caption="Sensory data summary")
```

## Part b
```{r, include=FALSE}
    ########################### 
    #Problem5_LongJump_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat"
    LongJump_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    colnames(LongJump_raw)<-rep(c("V1","V2"),4)
    LongJump_tidy<-rbind(LongJump_raw[,1:2],LongJump_raw[,3:4],
                             LongJump_raw[,5:6],LongJump_raw[,7:8])
    LongJump_tidy<-LongJump_tidy %>%  
        filter(!(is.na(V1))) %>%
        mutate(YearCode=V1, Year=V1+1900, dist=V2) %>%
        select(-V1,-V2)
    
    ########################### 
```

```{r, echo=FALSE}
knitr::kable(summary(LongJump_tidy), caption="Long Jump data summary")
```

## Part c
```{r, include=FALSE}
########################### 
    #Problem5_BrainBody_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat"
    BrainBody_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    colnames(BrainBody_raw)<-rep(c("Brain","Body"),3)
    BrainBody_tidy<-rbind(BrainBody_raw[,1:2],BrainBody_raw[,3:4],
                             BrainBody_raw[,5:6])
    BrainBody_tidy<-BrainBody_tidy %>%  
        filter(!(is.na(Brain))) 
    
    ########################### 
```

```{r, echo=FALSE}
    knitr::kable(summary(BrainBody_tidy), caption="Brain/Body weight data summary")
```


## Part d
```{r, include=FALSE}
    ########################### 
    #Problem5_Tomato_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat"
    Tomato_raw<-read.table(url, header=F, skip=2, fill=T, stringsAsFactors = F, comment.char = "")
    Tomato_tidy<-Tomato_raw %>%  
        separate(V2,into=paste("C10000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        separate(V3,into=paste("C20000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        separate(V4,into=paste("C30000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        mutate(C10000_3=gsub(",","",C10000_3)) %>%
        gather(Clone,value,C10000_1:C30000_3) %>%
        mutate(Variety=V1, Clone=gsub("C","",Clone)) %>%
        mutate(Variety=gsub("\\\\#"," ",Variety)) %>%
        separate(Clone,into = c("Clone","Replicate")) %>%
        select(-V1,Variety,Clone,value) %>%
        arrange(Variety) 
        
    ########################### 
```

```{r, echo=FALSE}
    knitr::kable(summary(Tomato_tidy), caption="Tomato data summary")
```


# Problem 6

After importing the data, there are three columns related to our analysis. The mean pH value is adopted to combine pH_min and pH_max. So the problem is transformed to test the relationship between pH mean values and foliage colors. 
```{r, include=FALSE}
# Path to data
library(swirl)
.datapath <- file.path(path.package('swirl'), 'Courses',
'R_Programming_E', 'Looking_at_Data',
'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")
# Remove annoying columns
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]
# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
'Foliage_Color', 'pH_Min', 'pH_Max',
'Precip_Min', 'Precip_Max',
'Shade_Tolerance', 'Temp_Min_F')

```

The colors are symbolized with numbers from 1 to 6 according to their mean values, as shown below. Then the scattor plot could be drawn to show the distribution. \

```{r, echo=FALSE}
color <- c('Dark Green','Yellow-Green','Green','Gray-Green','Red','White-Gray')
No <- c(1,2,3,4,5,6)
Relation <- cbind(color,No)
 knitr::kable(Relation, caption="Color Representation")

```

```{r,  echo=FALSE}
plants_2 <- plants[,c('Foliage_Color','pH_Min','pH_Max')]
plants_3 <- na.omit(plants_2)


#color_list <- levels(factor(plants_3$Foliage_Color))


pH_mean <- (plants_3$pH_Min + plants_3$pH_Max)/2
plants_4 <- cbind(pH_mean,plants_3)

# Dark Green  Yellow-Green  Green   Gray-Green    Red   White-Gray
# 1           2             3       4             5     6
color_code <- gsub('Dark Green', '1', plants_3$Foliage_Color, fixed=TRUE)
color_code <- gsub('Yellow-Green', '2', color_code, fixed=TRUE)
color_code <- gsub('Gray-Green', '4', color_code, fixed=TRUE)
color_code <- gsub('Red', '5', color_code, fixed=TRUE)
color_code <- gsub('White-Gray', '6', color_code, fixed=TRUE)
color_code <- gsub('Green', '3', color_code, fixed=TRUE)

plants_5 <- cbind(plants_4,color_code)
pH <- as.numeric(plants_5[,1])
color <- as.numeric(plants_5[,5])

plot(pH,color)
```

The lm function is used to build the linear model between pH and color. The coefficients are listed below.
```{r, echo=FALSE}

plants_6 <- cbind(pH,color)

fit <- lm(color ~ pH,data.frame(plants_6))
summary(fit)
```

Meanwhile, the ANOVA method is tried to explore the relationship, with details below.
```{r, echo=FALSE}
fit2 <- aov(color ~ pH)
summary(fit2)
```

# Problem 7
## Part d
Through the summary of data in 2017, there are 354 makes and 22275 models.\


## Part e
Use sort function to rank the defects. The largest five defects could be identified as followed.\

K04    AC1    G05    RA2    K05\
409467 323375 182410 177706 154179\

The top make/model for these defects are:
```{r, echo=FALSE}
Defect <- c('K04','AC1','G05','RA2','K05')
Make_Model <- c('VOLKSWAGEN/POLO','VOLKSWAGEN/POLO','VOLKSWAGEN/POLO','PEUGEOT/206; 1.4 3DRS','VOLKSWAGEN/POLO')
Relation <- cbind(Defect,Make_Model)
 knitr::kable(Relation, caption="TOP Make/Models of Five Common Defects")

```


## Part h
This workflow considers all the possible records at first, which lead to high volume of computing capacity. So if the contraint could be applied at first, such as the year 2017, the sample could be reduced a lot. 

